Optimal Fitting of Planar Curves to Prescribed Constraints

### 2014-02-02 idp/documents/documentation/paper.tex
split more illustrations into subfloats

				\begin{figure}[htb]
					\centering
					\includegraphics[width=\textwidth]{content/output/fairness_mec.pdf}
					\caption{Minimum Energy Curve Examples. Point specification items are displayed as red dots, direction specification items are displayed as green tangent lines.}
					\label{figure:minimum_energy_curve_examples}
				\end{figure}

@@

				\begin{figure}[htb]
					\centering
					\includegraphics[width=\textwidth]{content/output/fairness_mvc.pdf}
					\caption{Minimum Variation Curve Examples. Point specification items are displayed as red dots, direction specification items are displayed as green tangent lines.}
					\label{figure:minimum_variation_curve_examples}
				\end{figure}

>>>>

				\begin{figure}[htb]
					\centering
					\begin{subfigure}[b]{\textwidth / 3}
						\includegraphics[width=\textwidth]{content/output/fairness_mec_1.pdf}
					\end{subfigure}%
					\begin{subfigure}[b]{\textwidth / 3}
						\includegraphics[width=\textwidth]{content/output/fairness_mec_2.pdf}
					\end{subfigure}%
					\begin{subfigure}[b]{\textwidth / 3}
						\includegraphics[width=\textwidth]{content/output/fairness_mec_3.pdf}
					\end{subfigure}
					\caption{Minimum Energy Curve Examples. Point specification items are displayed as red dots, direction specification items are displayed as green tangent lines.}
					\label{figure:minimum_energy_curve_examples}
				\end{figure}

@@

				\begin{figure}[htb]
					\centering
					\begin{subfigure}[b]{\textwidth / 3}
						\includegraphics[width=\textwidth]{content/output/fairness_mvc_1.pdf}
					\end{subfigure}%
					\begin{subfigure}[b]{\textwidth / 3}
						\includegraphics[width=\textwidth]{content/output/fairness_mvc_2.pdf}
					\end{subfigure}%
					\begin{subfigure}[b]{\textwidth / 3}
						\includegraphics[width=\textwidth]{content/output/fairness_mvc_3.pdf}
					\end{subfigure}
					\caption{Minimum Variation Curve Examples. Point specification items are displayed as red dots, direction specification items are displayed as green tangent lines.}
					\label{figure:minimum_variation_curve_examples}
				\end{figure}
